### 2012-04-09 tr-semanticsearchsurvey-data/overview.tex

\subsection{Semantic Metadata}
Basically, semantic metadata is semantic data that captures information about the objects to be retrieved. Because it is clear from the context, these two terms are often used synonymously (in this work). Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published. Moreover, it may capture the semantics of the information contained in these objects. For instance, if a particular Web page is about a restaurant, its metadata may contain a structured description of that restaurant (as RDFa) corresponding to the text contained in the page. In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata. Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+. Semantic metadata representing the content may also be manually produced and embedded into the objects. Recently, several industry projects such as Google Rich Snippets and Yahoo! SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages. Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data. In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).

@@

Beyond direct matching and disambiguation, state-of-the-art techniques employ complex matching rules (or matching patterns in general), especially for the more complex task of relation extraction. Given a pattern like \verb+Mr. ? works for ?+, matching texts can be identified and relevant entities and relations can be extracted. Matching patterns are specified manually or learned automatically through machine learning techniques for pattern induction. Current state-of-the-art information extraction programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g. orthographic features such as whether the word contain digits or hyphens, word types such as lowercased and capitalized and syntactic features such as POS information), from the context (i.e. words in a text window along with their tags, labels etc.) as well as from background knowledge (e.g. from Gazetteers). These features along with labeled training examples are then used to train a classifier (one for every entity / relation type) or a probabilistic sequence model such as the Conditional Random Field~\cite{DBLP:conf/icml/ZhuNWZM05}. Besides these learning methods proposed for targeted information extraction, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open information extraction~\cite{DBLP:conf/ijcai/EtzioniFCSM11}. So far, semantic search systems focus on the use of targeted information extraction tools (e.g. IBM's UIMA, SOFIE~\cite{DBLP:conf/www/SuchanekSW09}). While they provide lower coverage, the quality of extracted outputs is higher compared to open information extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}. Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube.

@@

\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
Semantic search has been investigated from different communities in different contexts. In the IR community, semantic search has mainly been viewed from the perspective of document retrieval. Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data. Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources. Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information. Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers. We will now discuss these main types of approaches, several example systems, the ways they use semantics, as well as their reported performances. The classification of selected approaches into types is presented in Table~\ref{}. Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey.

% Table generated by Excel2LaTeX from sheet 'Tabelle5'
\begin{table*}[htbp]
  \centering
  \caption{Classification of approaches into types.}
    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
    \hline
    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. NL}} \bigstrut\\
\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
    \hline
    \hline
    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07} \bigstrut\\
    \hline
    \end{tabular}%
  \label{tab:approaches}%
\end{table*}%

@@

\textbf{Examples:} The \emph{NCBO Resource Index}\footnote{\url{http://
bioportal.bioontology.org/resources}}~\cite{DBLP:journals/ws/JonquetLFCNMS11} leverages the large amount of ontologies that exist in the biomedical domain. While some (of the 200 ontologies currently used) may capture more advanced semantics, they all are treated as lexical models consisting of connected concepts. Besides retrieval, concepts detected in documents are also used for concept-based iterative query construction and navigation, where similar to facets, users can add concepts to refine the queries and to browse documents along concepts, respectively.

\subsection{Annotation-based Document Retrieval} This encompasses the newer type of approaches, which exploit advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively). This query interpretation has has been applied both to keywords~\cite{} and NL questions~\cite{}. That is, this category covers both keyword search and NL question answering over documents.

@@

\textbf{Example:}
IBM Avatar, WATSON, question answering ~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}

\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for entities representing real-world objects (anything objects but documents). It includes search over (1) documents (e.g. for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), \dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} (2) over 
%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
%over (3) 
Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g. for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g. for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).

@@

\textbf{Example:}
Ask Gianluca, Sig.ma~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, Yahoo!, EntityCube

@@

\subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}

@@

  \caption{Classification of systems into aspects.}

>>>>

\subsection{Semantic Metadata}
Basically, semantic metadata is semantic data that captures information about the objects to be retrieved. Later, we also use the term \emph{documentation annotation} to refer to metadata created for text. Metadata include basic information about the objects such as \verb+author+ and the \verb+year+ it was published. Moreover, it may capture the semantics of the information contained in these objects. For instance, if a particular Web page is about a restaurant, its metadata may contain a structured description of that restaurant (as RDFa) corresponding to the text contained in the page. In fact, one main challenge in semantic search is to interpret the semantics behind the content of information objects and to represent it as semantic metadata. Not only entities may be recognized but for instance, the content of a document may be interpreted as referring to a \verb+meeting+ with the two \verb+researchers+ \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participants+. Semantic metadata representing the content may also be manually produced and embedded into the objects. Recently, several industry projects such as Google Rich Snippets and Yahoo! SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages. Complementary to this,  schema.org\footnote{\url{http://schema.org/}} is an initiative promoted by major Web search companies (Google, Microsoft, Yahoo!) aiming at the provision of a common vocabulary that can be used by site owners to capture their data. In this regard, we note that while Wikipedia can be conceived as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).

@@

Beyond direct matching and disambiguation, state-of-the-art techniques employ complex matching rules (or matching patterns in general), especially for the more complex task of relation extraction. Given a pattern like \verb+Mr. ? works for ?+, matching texts can be identified and relevant entities and relations can be extracted. Matching patterns are specified manually or learned automatically through machine learning techniques for pattern induction. Current state-of-the-art information extraction programs in fact, not only use simple word patterns, but complex combination of features derived from the words (e.g. orthographic features such as whether the word contain digits or hyphens, word types such as lowercased and capitalized and syntactic features such as POS information), from the context (i.e. words in a text window along with their tags, labels etc.) as well as from background knowledge (e.g. from Gazetteers). These features along with labeled training examples are then used to train a classifier (one for every entity / relation type) or a probabilistic sequence model such as the Conditional Random Field~\cite{DBLP:conf/icml/ZhuNWZM05}. Besides these learning methods proposed for targeted information extraction, which assume a fixed set of predefined types of entities / relations to be extracted, there are also proposals for open information extraction~\cite{DBLP:conf/ijcai/EtzioniFCSM11}. So far, semantic search systems focus on the use of targeted information extraction tools (e.g. IBM's UIMA, SOFIE~\cite{DBLP:conf/www/SuchanekSW09}). While they provide lower coverage, the quality of extracted outputs is higher compared to open information extraction tools, an aspect shown to be very influential in improving the precision of semantic search results~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06,DBLP:conf/cikm/Chu-CarrollP07}. Promising is the combined usage of targeted and open information extraction, a direction currently pursuit by Microsoft's EntityCube~\cite{DBLP:conf/www/ZhuNLZW09}.

@@

\section{Main Types of Approaches and Their Performances}\label{sec:approaches}	
Semantic search has been investigated from different communities in different contexts. In the IR community, semantic search has mainly been viewed from the perspective of document retrieval. Here, classic \emph{concept}-based approaches based on the use of lexical models can be distinguished from more recent approaches that leverage document \emph{annotations} in the form of semantic data. Another line of research is \emph{entity} search, which has been studied in the context of entities extracted from Web pages, Wikipedia pages corresponding to entities, as well as entities captured by databases and semantic data sources. Another popular topic is keyword search over databases and semantic data, which is mainly about \emph{relational} information. Last but not least, the processing of NL queries over these semantic data entails specific challenges and opportunities, which has attracted interests from a specific community of researchers. We will now discuss these main types of approaches, several example systems, the ways they use semantics, as well as their reported performances. The classification of selected approaches into types is presented in Table~\ref{}. Further, Table~\ref{tab:examples} provides an overview of selected systems and their classification along the main aspects of semantic search discussed in this survey. Since the technique used within the same system is similar for document and query interpretation, we omit this distinction in Table~\ref{tab:examples}.

\dtr{Say what  systems do with respect to aspects}

% Table generated by Excel2LaTeX from sheet 'Tabelle5'
\begin{table*}[htbp]
  \centering
  \caption{Classification of selected approaches into types.}
    \begin{tabular}{|p{2cm}|p{1.5cm}|p{2cm}|p{1.5cm}|p{1.5cm}|p{2cm}|p{2cm}|p{1.5cm}|}
    \hline
    \multicolumn{1}{|c|}{\multirow{2}[4]{*}{Concept-based}} & \multicolumn{2}{c|}{Annotation-based} & \multicolumn{3}{c|}{Entity Search} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. Keyword}} & \multicolumn{1}{c|}{\multirow{2}[4]{*}{Rel. NL}} \bigstrut\\
\cline{2-6}    \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{NL} & \multicolumn{1}{c|}{Keyword } & \multicolumn{1}{c|}{Document} & \multicolumn{1}{c|}{Wikipedia} & \multicolumn{1}{c|}{Semantic Data} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} \bigstrut\\
    \hline
    \hline
    \cite{DBLP:conf/sigir/Giger88, DBLP:conf/esws/GiunchigliaKZ09, DBLP:conf/sigir/QiuF93, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/TrieschniggKS06, DBLP:conf/trec/ZhouYTS06,  DBLP:journals/ws/JonquetLFCNMS11, DBLP:conf/trec/JelierSEWMSMK03, DBLP:conf/sigir/Voorhees93, DBLP:conf/sigir/Voorhees94, DBLP:journals/ipm/MeijTRK10} & \cite{DBLP:conf/sigir/Chu-CarrollPCFD06, DBLP:journals/tkde/CastellsFV07, DBLP:journals/ws/FernandezCLVCM11, tran2007expressive, DBLP:conf/cikm/Chu-CarrollP07} &  	  \cite{DBLP:journals/tkde/CastellsFV07, DBLP:conf/sigmod/KandoganKRVZ06, tran2007expressive, DBLP:conf/aaai/JiangT06, DBLP:series/sci/NgoC10, DBLP:conf/www/RochaSA04, DBLP:conf/esws/SchumacherSS08, DBLP:conf/www/GuhaMM03} & \cite{DBLP:journals/ipm/BalogAR09, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/sigir/Chu-CarrollPCFD06} & \cite{DBLP:journals/tois/BalogBR11, DBLP:conf/cikm/KapteinSVK10, DBLP:conf/cikm/BronBR10, DBLP:conf/ecir/PehcevskiVT08} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/sigir/BastCSW07, DBLP:conf/semweb/BlancoMV11, DBLP:journals/ijswis/ChengQ09, DBLP:journals/ws/TummarelloCCDDD10, DBLP:conf/eswc/Tran12,DBLP:conf/www/NieMSWM07, DBLP:conf/www/NieZWM05} & \cite{DBLP:conf/vldb/BalminHP04, DBLP:conf/cikm/BicerTN11, DBLP:conf/cikm/CoffmanW11, DBLP:journals/debu/ElbassuoniRSW10, DBLP:journals/ws/TranWH09, DBLP:journals/ws/TranHL11, DBLP:conf/icde/KasneciSIRW08, DBLP:conf/sigmod/LiJLF09, DBLP:conf/cikm/LadwigT11} & \cite{DBLP:conf/aswc/CaoCT08, DBLP:journals/dke/CimianoHHMS08, DBLP:conf/esws/WangXZY07, DBLP:conf/esws/DamljanovicAC10, DBLP:journals/ws/LopezUMP07} \bigstrut\\
    \hline
    \end{tabular}%
  \label{tab:approaches}%
\end{table*}%

@@

\textbf{Examples:} While concepts may not directly help to improve relevance-based metrics such as precision and recall, there are many systems showing they can provide other benefits, such as for iterative concept-based query refinement or for browsing. These features are available with \emph{gopubmed} for instance. Targeting the same domain, the \emph{NCBO Resource Index}\footnote{\url{http://
bioportal.bioontology.org/resources}}~\cite{DBLP:journals/ws/JonquetLFCNMS11} leverages the large amount of ontologies that exist in the biomedical domain. While some (of the 200 ontologies currently used) may capture more advanced semantics, they all are treated as lexical models consisting of connected concepts. Besides retrieval, concepts detected in documents are also used for concept-based iterative query construction and navigation, where similar to facets, users can add concepts to refine the queries and to browse documents along concepts, respectively. Targeting the Web scenario, \emph{Hakia}\footnote{\url{http://hakia.com/}} (Hak) uses a cross-domain lexical model called the Commercial Ontology, which hierarchically organizes word senses at three different layers. Based on these concepts, Hakia interprets the content as ``knowledge bits'', and for efficiency reason, extracts and indexes all possible queries that can be constructed from them. The concepts and ontology are used for retrieval, for handling syntactic variants in keywords and NL queries (morphological variants, synonyms, generalization) in particular.

\subsection{Annotation-based Document Retrieval} These approaches exploit the advancement in information extraction technologies to obtain a richer representation of queries and documents, namely as \emph{entities} and \emph{relations} represented as annotations (query and document annotations, respectively). As shown in Table~\ref{tab:approaches}, this query interpretation has has been applied both to keywords and NL questions. 
%That is, this category covers both keyword search and NL question answering over documents.

@@

\textbf{Examples:}
IBM's \emph{AVATAR}\footnote{now superseeded by SystemT, \url{http://www.almaden.ibm.com/cs/projects/avatar/}} (AVA), is an example of keyword search over documents, which uses UIMA for extracting annotations. It interprets keywords as a structure query, which is then processed against a database of annotations. As answers, the system does not return documents, but annotations representing information about entities and relations extracted from documents. In addition to annotations, other structured datasets (semantic data) can be used for search. \emph{Powerset} (PS) performs information extraction also to return information about entities and relations (to queries represented as keywords as well as NL). Its demo constructed for a subset of Wikipedia also returns pages as results. More focused towards the processing of complex NL inputs is Watson~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} (J!). It targets the Jeopardy! quiz show, where the task is basically, to find factual answers related to entities, given the category and several clues. It is a complex system combining different techniques. The starting points are previous IBM works, the PIQUANT system for combining evidences~\cite{DBLP:conf/naacl/Chu-CarrollCPI03} and the GuruQA for using annotations~\cite{DBLP:conf/sigir/PragerBCR00,DBLP:conf/sigir/Chu-CarrollPCFD06} in question answering in particular. Besides question and content analysis to interpret the meaning in terms of entities and relations, the system also implements techniques not covered by this survey, such as corpus expansion (to identify and acquire sources of content on the Web, both unstructured Web documents as well semantic data such as YAGO) and question decomposition and classification (identify parts and types of questions that need special processing, e.g. a math question). Computing results requires merging partial evidences as well as their confidence values. Similar to learning to rank, a machine learning method is used for the combination. Watson also uses the semantics in some sources to perform reasoning, e.g. it exploits subsumption and
disjointness in type taxonomies and applies geospatial and
temporal reasoning. While geospatial reasoning is used
to deal with spatial
relations such as directionality, borders, and
containment between geo-entities (e.g. when asked for an Asian city, then spatial containment
provides evidence that Beijing is suitable, whereas Sydney is not), temporal reasoning helps to deal with 
inconsistencies between dates in clues and answers.

\subsection{Entity Search} While the two mentioned types retrieve documents, this type of approaches search for entities representing real-world objects (anything objects but documents). It includes search over (1) documents (e.g. for processing entity-related factoid and list queries of the TREC Question Answering track~\cite{DBLP:conf/sigir/Chu-CarrollPCFD06}, or expert search queries of the TREC Enterprise track~\cite{DBLP:journals/ipm/BalogAR09}), 
%\dtr{todo: A particular type of entity search, expert retrieval has been the focus of a number of evaluations; also belong to the type of entity search that mainly operates on documents; + some other features?.} 
(2) over 
%documents associated with metadata, (for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), 
%over (3) 
Wikipedia data, which as discussed, can be seen as a kind of semantic data (e.g. for answering entity-related queries of the INEX Entity Ranking track~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/ecir/PehcevskiVT08}), or over pure (3) semantic data crawled from the Web (e.g. for answering entity queries of the SemSearch Entity track~\cite{DBLP:conf/semweb/BlancoMV11}).

@@

\textbf{Examples:}
Systems searching for entity related information extracted from documents include \emph{AVATAR}, \emph{Powerset} and \emph{Watson}. Targeting Wikipedia documents, \emph{SERWi}~\footnote{\url{http://godzilla.kbs.uni-hannover.de:8089/ER08Demo/}} (SER) runs on top of subsets used at INEX XER 2007 and 2008. It exploits category information treated as part of a knowledge model to interpret entity queries expressed as keywords, and returns a ranked list of entities represented by their Wikipedia pages. For the semantic data case, we have \emph{Sig.ma} as one representative system, which provides keyword querying capabilities over an index of semantic data sources. For query answering, it matches query terms against an inverted index of entity descriptions, presents the sources for which matches could be found, and also, allow users to approve or reject certain sources of information. As illustrated in Fig.~\ref{fig:screenshot_yahoo}, Yahoo! (Y!) also employs semantic data for entity search. It uses its own curated sources of semantic data (e.g. data about companies) to provide -- in addition to relevant Web pages -- specific information about the requested entity and links to related entities. Microsoft's \emph{EntityCube} (MS) extracts information from text~\cite{DBLP:conf/www/ZhuNLZW09} to support entity-related keyword queries over documents and extracted information. For every query, it displays matching documents and entity information, and allows users to refine results based on facets representing related entities. As opposed to Yahoo!, which uses BM25F for ranking~\cite{DBLP:conf/semweb/BlancoMV11}, it uses language models for query-relevance~\cite{DBLP:conf/www/NieMSWM07} and also, PopRank for centrality-based ranking~\cite{DBLP:conf/www/NieZWM05}.

@@

\textbf{Examples:} \emph{AVATAR} in fact, not only can search over annotations but any kinds of semantic data. The structured queries AVATAR obtains from keywords may also involve relational information. Another system is \emph{SemSearchPro} (SPro), which exploits semantics throughout the search process: It uses lexical and knowledge models as well as the semantic data to translate keyword queries to SPARQL queries (interpretation), to find connections between entities mentioned in the keyword query and for processing fully structured SPARQL queries (matching), and to rank results based on structure-based proximity, centrality and query-relevance (ranking). As illustrated in Fig.~\ref{fig:screenshot_iwb}, it also supports faceted search, and iterative query construction where users can iteratively build complexer queries by selecting suggested terms and query completions as they type. TASTIER~\footnote{\url{http://tastier.ics.uci.edu/}} also supports this auto-completion search, suggesting results as users type. The relational search demo is available for DBLP~\footnote{\url{http://dblp.ics.uci.edu/}}, a dataset containing information about entities in the bibliographic domain.

\subsection{Relational NL Search} \dtr{are there benchmarks for NL QA over data?}
As opposed to NL search over documents (mainly studied by IR researchers), this topic attracts a separate community that deals with interfaces over databases and knowledge bases (expert systems). NL search

@@

  \caption{Classification of selected systems into aspects.}
